Technology-based aids for people affected by Autism Spectrum Disorder (ASD)

### 2017-11-23 paper.tex
Removed AVATAR general section and integrated the other

%TODO Avatar-based techniques to improve the performances of the therapy
%TODO Methods to detect the anxiety level
To improve the performance of the sessions, the use of \gls{va} platforms has been introducted.
A \gls{va} platform consists of an avatar, that can be a robot or a virtual character, a learning software that receives information from the Avatar, elaborates them and adjusts the response of the Avatar, and an interface for the therapist that interprets the results.
In a \gls{va} session the therapist, with the aids of the learning software, trains the Avatar to do an action that the child has to imitate. At the same time, the child tries to imitate the Avatar learning new ways to interact with the society.
Different system has been proposed, we describe here two different solutions, one more general and one more complex and efficient.

\subsection{General AVATAR idea}
\label{sec:avatar_general}

\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{avatar_system.png}
\caption{Scheme of AVATAR system}
\label{fig:avatar_scheme}
\end{minipage}
\begin{minipage}{0.48\textwidth}
\centering
\includegraphics[width=\textwidth]{avatar_tasks.png}
\caption{Structure of AVATAR platform}
\label{fig:avatar_tasks}
\end{minipage}

The idea of an Avatar-based therapy session is shown firstly in \cite{Guerrero-vasquez}. In the paper they propose a system composed by a \gls{va} and an \textit{expert system} used by the therapist to instruct the \gls{va}. A general scheme of the system is shown in \autoref{fig:avatar_scheme}.

They chose to use a Virtual Agent instead of a robot since, according with the needs, it provides the possibility to customize the tool, while a robot is limited by its structure and its \gls{dof}.

As can be seen in \autoref{fig:avatar_tasks}, the platform is organized as follows:
\begin{LaTeXdescription}
	\item[Child Interface] It selects the child's favorite Virtual Agent and uses interaction tools as screen, camera, microphone and speakers to interact with the child;
	\item[Expert System] Contains a learning algorithm that promotes interaction between the child and the Virtual Agent, it stores the scenario and features of the Virtual Agent and it monitors progress of the session in order to generate statistical reports that will be used by the therapist;
	\item[Therapist Interface] Allow the therapist to access to the reports generated by the Expert System and gives information about the current therapy, in order to allow the therapist to draw conclusions.
\end{LaTeXdescription}

The choices about the best \gls{va} to use during the sessions, or the characteristics that has to be changed in the current \gls{va}, are taken monitoring the reaction of the child when he is put in front of them.
It is not necessary for the character to be a human, since the highest degree of affinity can be towards an animal or an object.

The key point in this work is that the information received on the screen of the therapist interface shows a real time image of the child and monitored progress statistics.
Since the VA that the child observes on his screen is his therapist in disguise, actually it is the therapist who, combined with artificial intelligence, promotes the interaction in combination with the expert system.

\subsection{A more complex system}
\label{sec:avatar_complex}

Another more complex and complete approach was performed in \cite{Alahbabi17}, using a robot instead of a \gls{va}; this because it has been shown in \cite{Pioggia08} that patients manifest a more favorable response towards humanoid robots than to other non-humanoid virtual characters.

This approach has sensible advantages but also some intrinsic shortcomings:
\begin{itemize}
	\item most of the robotic or virtualized therapies are preprogrammed and this makes the session boring and repetitive;
	\item robots are limited and work in a controlled environment;
	\item usually robots do not have a quantitative behavioral analysis tool, due to the absence of therapists during their development process.
\end{itemize}

@@

The movements performed by the robot and imitated by the child are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.

During the session, points are given to the child as he progresses and performs the right movement at the right time.
The total score is given by the sum of three contributes:

\begin{LaTeXdescription}
	\item[Motion Score] Is relative to the goodness of the movement made by the patient to imitate the robot;
	\item[Attention Score] the child takes one point for each second he's looking at the robot’s face whenever the robot is asking him a question;
	\item[Response Score] for this score, points are given for the delay time between the moment in which the robot asks a question and moment in which the child start answering the questions.
	10 points are given for the first 10 seconds after the robot/therapist stops talking, and one point is subtracted for each second of delay.
\end{LaTeXdescription}

>>>>

%TODO Avatar-based techniques to improve the performances of the therapy
%TODO Methods to detect the anxiety level
To improve the performance of the sessions, the use of \gls{va} platforms has been introducted.
A \gls{va} platform consists of an Avatar, that can be a robot or a virtual character, a learning software that receives information from the Avatar, elaborates them and adjusts the response of the Avatar, and an interface for the therapist that interprets the results.
In a \gls{va} session the therapist, with the aids of the learning software, trains the Avatar to do an action that the child has to imitate. At the same time, the child tries to imitate the Avatar learning new ways to interact with the society.

Different system has been proposed, we describe here two solutions based on an Avatar, the first is a robotic one while the second is virtual and adapts the tasks proposed in function of the child's anxiety level.

\subsection{Robotic-based therapy}
\label{sec:robotic}

The first solution was proposed in \cite{Alahbabi17}, using a robotic Avatar.
They chose a robotic-based solution since it has been shown in \cite{Pioggia08} that patients manifest a more favorable response towards humanoid robots than to other non-humanoid virtual characters.

This approach has sensible advantages if compared with classical therapies, but it has also some intrinsic shortcomings:
\begin{itemize}
	\item most of the robotic or virtualized therapies are preprogrammed and this makes the session boring and repetitive;
	\item robots are limited and work in a controlled environment;
	\item usually robots do not have a quantitative behavioral analysis tool, due to the absence of therapists during their development process.
\end{itemize}

@@

The movements performed by the robot and imitated by the child and the therapist's questions are specifically selected to teach the child how to interact with other people and to improve his response to social stimolous.

During the session, points are given to the child as he progresses and performs the right movement at the right time or if he gives an acceptable answer to a question.
The total score is given by the sum of three contributes:

\begin{LaTeXdescription}
	\item[Motion Score] is relative to the goodness of the movement made by the patient to imitate the robot;
	\item[Attention Score] the child takes one point for each second he's looking at the robot’s face whenever the robot is asking him a question;
	\item[Response Score] for this score, points are given for the delay time between the moment in which the robot asks a question and moment in which the child start answering the questions.
	10 points are given for the first 10 seconds after the robot/therapist stops talking, and one point is subtracted for each second of delay.
\end{LaTeXdescription}
